The Supervisionary proof-checking kernel

### 2021-10-08 paper/prisc-2022.tex
prisc-2022: moved proof-asssitant section up

We have described the \emph{what} of Supervisionary and now turn our attention to the \emph{why}.
This can be approached by examining Supervisionary both as a programming platform, and as a proof-assistant kernel.
What follows is largely speculative, and a work-in-progress.

@@

LCF-style interaction is centred around the REPL of the meta-language, or some thin layer built atop, itself started from an operating system shell---a kind of shell within a shell.
Our design allows us to dispense with this middle-man, and develop proofs interactively directly in a shell implemented on top of our kernel.
Moreover our kernel inherently internalises kernel objects, and could therefore make them available to browse as special files within a hierarchical filesystem, as discussed previously, in analogy to how Linux exposes its internals as special files---for example, the contents of \texttt{/proc/} and \texttt{/dev/}.
In this way, related material could appear grouped in directories, searched using command-line utilities, or opened by a process for use at runtime.

>>>>

We have described the \emph{what} of Supervisionary and now turn our attention to the \emph{why}.
This can be approached by examining Supervisionary both as a proof-assistant kernel, and as a programming platform.
What follows is largely speculative, and a work-in-progress.

LCF-style interaction is centred around the REPL of the meta-language, or some thin layer built atop, itself started from an operating system shell---a kind of shell within a shell.
Our design allows us to dispense with this middle-man, and develop proofs interactively directly in a shell implemented on top of our kernel.
Moreover our kernel inherently internalises kernel objects, and could therefore make them available to browse as special files within a hierarchical filesystem, as discussed below, in analogy to how Linux exposes its internals as special files---for example, the contents of \texttt{/proc/} and \texttt{/dev/}.
In this way, related material could appear grouped in directories, searched using command-line utilities, or opened by a process for use at runtime.

@@
